EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-22 05_examples.tex
Updates from Overleaf

\begin{figure}%[t!]
  \includegraphics[width=\linewidth]{figures/figBetheW2D.pdf}
    \caption{\label{figEx1W}%
    \textbf{Finite temperature DMFT solution.}
    Comparison of the imaginary parts of the Green's function $\Im{G}(i\omega_n)$ and Self-energy $\Im{\Sigma}(i\omega_n)$ from different solutions of the Hubbard model on the Bethe lattice using DMFT. Data are for $T/D=0.01$ and $U/D=2.0$. CTQMC results from the solver included with w2dynamics are compared against \NAME ED results, used both through the w2dynamics interface and with a standalone Fortran program. \fixme{Are we sure we want to use these
    fancy markers? As I saw the earlier version, I know what they are doing and I understand that all data coincide perfectly and how this can make for a fancy plot. But I suspect that looking at it without any prior knowledge, at a glance, I would just desume that the w2d and edipack calculations are not matching. I would probably just go with the usual "x", "." and "+" markers, that all together make for a fancy multicolor "*". The dot in front of everything, with the most fluo color (e.g. bright green). The "x" and "+" in complementary colors, like blue and red, not in fluo version, so that they do not "hide" the dot. Something like that.}
        }
\end{figure}

>>>>

\begin{figure}%[t!]
  \includegraphics[width=\linewidth]{figures/figBetheW2D.pdf}
    \caption{\label{figEx1W}%
    \textbf{Finite temperature DMFT solution.}
    Comparison of the imaginary parts of the Green's function $\Im{G}(i\omega_n)$ and Self-energy $\Im{\Sigma}(i\omega_n)$ from different solutions of the Hubbard model on the Bethe lattice using DMFT. Data are for $T/D=0.01$ and $U/D=2.0$. CTQMC results from the solver included with w2dynamics are compared against \NAME ED results, used both through the w2dynamics interface and with a standalone Fortran program. 
    % \fixme{Are we sure we want to use these
    % fancy markers? As I saw the earlier version, I know what they are doing and I understand that all data coincide perfectly and how this can make for a fancy plot. But I suspect that looking at it without any prior knowledge, at a glance, I would just desume that the w2d and edipack calculations are not matching. I would probably just go with the usual "x", "." and "+" markers, that all together make for a fancy multicolor "*". The dot in front of everything, with the most fluo color (e.g. bright green). The "x" and "+" in complementary colors, like blue and red, not in fluo version, so that they do not "hide" the dot. Something like that.}
        }
\end{figure}
